Achieving Effective River Basin Governance through Institutional Shifts: Examining the Yellow River Basin's Social-Ecological Systems in China

### 2023-05-05 docs/papers/01_manuscript/01_introduction.tex
docs(introduction): :art: GPT润色语言

% 水竞争的重要性
Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally~\cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
In the context of climate change, the mismatches between supply and demand for water resources are expected to become increasingly more prominent~\cite{florke2018, yoon2021}.
Hence, large river basins are increasingly seeking for effective water governance solutions by coordinating stakeholders, providing water resources, and ensuring the sustainable allocation of shared water resources~\cite{wang2019d}.
As results, hydrological processes are tightly intertwined with societies, shown as an social-ecological system (SES) at a basin scale where complex socio-hydrological feedback merges SES structures.

Governing river basin systems involves reshaping their SES structures through institutions such as policies, laws, and norms~\cite{young2008,cumming2020b}.
Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{lien2020, bodin2017b}.
Effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, contributing to the sustainability of SES~\cite{epstein2015, wang2019d} (Figure~\ref{fig:framework}~\textbf{a}).
While some institutional advances have led to desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China~\cite{wang2019d}, and collaborative water governance systems in Europe~\cite{green2013}),
imposing institutional shifts may create or destroy connections and effectiveness are not ubiquitous~\cite{loos2022}. 
For example, Colorado River once had sever water shortage and costly water competition until confirming water rights with following water institutional system~\cite{hadjimichael2020}.  % TODO check this expression. 科罗拉多河的这个例子还要举得更好一些
Therefore, examining when and how an institution leads to effective water governance can bring crucial insights for sustainability in global river basins.

% match & mismatch
Recent studies explored various effects of institutions on river basins governance, while quantitative assessments with controlled comparisons are remaining scarce~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}.
Additionally, understanding how different SESs structures influence institutional effectiveness is challenging due to the complexity and dynamics of these systems~\cite{bodin2017b}.
Thus, the knowledge gap lies in the limited understanding of aligning institutions with SES structures to promote sustainable river basins governance.
It hinders designing effective institutions that address the diverse challenges and opportunities in various social-ecological contexts, ultimately impacting long-term sustainability.

@@

To gain a deeper understanding of how institutions align or misalign with their social-ecological context, we use the Yellow River Basin (YRB), China, as a case study to examine the consequences and incentives of two significant institutional shifts in water allocation: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulation (98-UBR).
These shifts considerably transformed the SES structures within the basin, and offered valuable insights for two main reasons:
(1) the top-down institutional shifts led to substantial changes in SES structures, allowing us to quantitatively estimate their net effects; and (2) the basin's unique experience of multiple radical institutional shifts provides a rare opportunity to compare natural experiments and understand the impacts of SES structural changes on water governance.

Our investigation of the consequences of YRB's institutional shifts involves analyzing quasi-natural experiments with causal inference approach.
First, we use data from official documents following the two institutional shifts to describe the YRB's SES structures' comparable changes between 1979 and 2008.
Next, we employ the ``Differenced Synthetic Control (DSC)'' method~\cite{arkhangelsky2021}, which accounts for economic growth and natural background, to estimate theoretical water use scenarios in the absence of institutional shifts.
This approach enables us to establish a counterfactual basis for exploring the consequences and incentives related to SES structures, thereby enhancing our understanding of institutions' potential role in global water governance.
% Finally, we develop a marginal benefits analysis approach to interpret the underlying processes of misaligned institutions based on SES structures.

>>>>

% 水竞争的重要性
Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally~\cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
Amidst climate change, mismatches between supply and demand for water resources are expected to become increasingly more prominent~\cite{florke2018, yoon2021}.
Consequently, large river basins are progressively seeking effective water governance solutions by coordinating stakeholders, providing water resources, and ensuring the sustainable allocation of shared water resources~\cite{wang2019d}.
In this way, hydrological processes are tightly intertwined with societies, forming a social-ecological system (SES) at a basin scale with complex socio-hydrological feedback.

Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{young2008, lien2020, bodin2017b, wang2022g}.
These interactions constitute a type of SES structure, where effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different interactions, contributing to sustainability~\cite{epstein2015, wang2019d}.
% (Figure~\ref{fig:framework}~\textbf{a}).
% Governing river basin systems involves reshaping their SES structures through institutions such as policies, laws, and norms~\cite{,cumming2020b}.
While some institutional advances have led to effective water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China~\cite{wang2019d}, and collaborative water governance systems in Europe~\cite{green2013}), imposing institutional shifts may create or destroy connections and effectiveness is not ubiquitous~\cite{loos2022}.
For example, the Colorado River once experienced severe water shortage, and institutions led to various shortage magnitudes for different stakeholders even under the same water demand levels~\cite{hadjimichael2020}.
Therefore, examining when and how an institution leads to effective water governance can bring crucial insights for the sustainability of river basins.

% match & mismatch
Recent studies have explored diverse effects of institutions on river basin governance~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}, while the current analysis is more about interpreting outcomes after the institutional changes but cannot compare how scenarios would be without these institutional changes.
Moreover, understanding how different SES structures influence institutional effectiveness is challenging due to the complexity and dynamics of socio-hydrological systems~\cite{bodin2017b}.
Thus, knowledge gaps lie in the limited understanding of effective alignments between institutional shifts and SES structures, hindering the design of effective policies to promote sustainable river basin governance.
To fill these knowledge gaps, we study the Yellow River basin, the fifth-largest river worldwide and one of the most anthropogenically altered river basins, to quantitatively measure the effects of changing SES structures.

@@

% 黄河的介绍
In the 1980s, intense water use, accounting for about $80\%$ of the Yellow River surface water, caused consecutive drying-up crises of runoff, leading to wetland shrinkage, agriculture reduction, and scrambles for water~\cite{wohlfart2016}.
To alleviate water stress, Chinese authorities implemented several ambitious water management policies in the Yellow River Basin (YRB), such as the South-to-North Water Diversion Project and the Water Resources Allocation Institutions~\cite{long2020, wang2019d}.
In this study, we specifically examined two significant institutional shifts in water allocation of the YRB\: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).
the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).
Instead of focusing on engineering and increasing water supply, the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, an authority at a basin level) mainly aimed to limit water demands~\cite{bouckaert2022, speed2013}.
These institutional shifts can offer valuable insights for two main reasons:
(1) the top-down institutional shifts suddenly led to transformations of SES structures, allowing us to quantitatively estimate their net effects; and (2) the two institutional shifts within the same river basin provide rare comparable quasi-natural experiments.

In this study, we portrayed changes of SES structures throughout the YRB's institutional shifts (the 87-WAS and the 98-UBR) and quantitatively investigated their consequences, followed by a discussion on the effectiveness of institutional shifts.
Specifically, we first used the descriptions of official documents following the two institutional shifts to abstract the interactions between main stakeholders and their river segment units for interpreting SES structure changes between 1979 and 2008.
Next, and perhaps most importantly, we employed the ``Differenced Synthetic Control (DSC)'' method~\cite{arkhangelsky2021}, which accounts for economic growth and natural background, to estimate theoretical water use volumes under scenarios absent of institutional shifts.
Finally, in the discussion, we linked the effectiveness of institutional shifts to the portrayed structures, by comparing the YRB's case to previous SES structure studies and developing a marginal benefits analysis.

### 2023-05-05 docs/papers/01_manuscript/study_area.tex
docs(introduction): :art: GPT润色语言

The YRB, cradle of Chinese civilization, locates in north-central China and crosses ten province-level regions whose socio-economic development highly depend on water from the Yellow River~\ref{fig:yrb}.
As semi-arid and arid region, YRB's annual precipitation varies from about $100$ to $1000~mm$ and increases from the northwest to the southeast, while annual pan evaporation varies from about $700$ to $1800~mm$~\cite{wang2022e}.
Taken together, YRB supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
Hence, over withdrawing water from the Yellow River became an urgent concern since the river began to dry up since early $1970s$.
Among the policies proposed for solving the problem, a series of water resource allocation institutions aimed to limit water use of each region into specific quotas, remarked as of the most important solutions.
However, few attempts quantitatively assessed how the YRB's water allocation scheme contributed to water governance, while other engineering solutions were carefully evaluated~\cite{long2020}.
% 出现报错是因为最后的大写结尾LaTeX无法判断是缩写还是一个句子结束，这里是句子结束所以加 \\
% https://tex.stackexchange.com/questions/55105/when-should-i-use-intersentence-spacing

@@

YRB was the first basin in China for which a water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level)\cite{wang2019a}:
(1) In $1980s$, the provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River~\cite{wang2019, wang2019a}.
(2) In $1987$, implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
(3) In $1998$, implementation of unified regulation. (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
% 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
(4) In $2008$, provinces are asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019,wang2019a}.
(5) In $2021$, a call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).

Our study period ranges from $1980$ (proposing the water quotas) to $2008$, when it started to completely establish a regulating system with quotas throughout basin, provincial, and district levels.
During the period, two significant institutional shifts can be analyzed by using documents of $1987$ (87-WAS) and $1998$ (98-UBR), which split the study period into three pieces: from 1980 to 1987 (before 87-WAS), from 1988 to 1997 (after 87-WAS and before 98-UBR), and from 1998 to 2007 (after 98-UBR).
% Those efforts led to ecological restoration of wetlands and the estuarine delta. Drying up has been avoided for over $20$ years, which is widely considered a substantial management achievement.

>>>>

The YRB, cradle of Chinese civilization, is located in north-central China and spans ten province-level regions whose socio-economic development heavily depends on water from the Yellow River.
As a semi-arid and arid region, the YRB's annual precipitation varies from about 100 to 1,000 mm and increases from the northwest to the southeast, while the annual pan evaporation varies from about 700 to 1,800 mm~\cite{wang2022e}.
Together, the YRB supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
Hence, over-withdrawing water from the Yellow River became an urgent concern when the river began to dry up in the early 1970s.
Among the policies proposed to address the problem, a series of water resource allocation institutions aimed to limit water use for each region with specific quotas, which were regarded as some of the most important solutions.
However, few attempts have been made to quantitatively assess how the YRB's water allocation scheme contributed to water governance, while other engineering solutions have been carefully evaluated~\cite{long2020}.
% 出现报错是因为最后的大写结尾LaTeX无法判断是缩写还是一个句子结束，这里是句子结束所以加 \\
% https://tex.stackexchange.com/questions/55105/when-should-i-use-intersentence-spacing

@@

The YRB was the first basin in China for which water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level):
(1) In $1980s$, proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019, wang2019a}.
(2) In $1987$, the Water Allocation Scheme was implemented (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
(3) In $1998$, the Unified Basinal Regulation was implemented (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
% 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
(4) In $2008$, provinces were asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019,wang2019a}.
(5) In $2021$, there was a call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).

Our study period therefore ranges from $1980$ (when water quotas were proposed) to $2008$, when a regulating system with quotas was fully established at basin, provincial, and district levels.
During this period, two significant institutional shifts can be analyzed using documents from $1987$ (87-WAS) and $1998$ (98-UBR), which split the study period into three sections: from $1980$ to $1987$ (before 87-WAS), from $1988$ to $1997$ (after 87-WAS and before 98-UBR), and from $1998$ to $2007$ (after 98-UBR).
% Those efforts led to ecological restoration of wetlands and the estuarine delta. Drying up has been avoided for over $20$ years, which is widely considered a substantial management achievement.
